---
title: "STATISTICAL TECHNIQUES"
author: '100594631'
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Loading up the Dataset into R-Markdown working environment
df <- read.csv('C:/Users/USER/Documents/Raw_Data/superstore_dataset2011-2015.csv')
head(df, 5)
```
THE METADATA::

Ship Mode=> Shipping Mode specified by the Customer. Segment => The segment where the Customer belongs. Region => Region where the Customer belong. Sales => Sales of the Product. Quantity => Quantity of the Product. Discount => Discount provided. Shipping Cost=> The amount required to transport the product Total Sales => The product of Sales and Quantity Sales After Discount => Total sales after discount deduction


```{r}
# Attaching the variables to the dataframe fro ease of calling
attach(df)
```

...
```{r}
# the properties of the dataset
str(df)
```
BRIEF EXPLORATORY ANALYSIS

(QUALITATIVE)

```{r}
#Viewing the frequency of the Segment Variable
Segment.freq <- table(Segment)
Freq_Dist <- cbind(Segment.freq)
Freq_Dist
```
...
```{r}
#the relative frequency distribution in then given by
Segment.relfreq <- Segment.freq/nrow(df)
Rel_Freq_Dist <- round(cbind(Segment.relfreq) * 100,2)
Rel_Freq_Dist
```


...
```{r}
#Segment Frequency Distribution
barplot((Segment.freq),
     col="red", border=3, 
     main="Segment Frequency Distribution", 
     xlab="Segment", 
     ylab="Frequency"
     )
```

QUANTITATIVE
```{r}
#Relative Fequency Disricution of the the variable Quantity.
range(Quantity)
breaks <- seq(1, 14, by = 1) 
breaks
```
...
```{r}
#Classify the Quantity according to the half-unit-length sub-intervals with cut
Quantity.cut <- cut(Quantity, breaks, right = FALSE)
```
...
```{r}
#frequency distribution of the quantity of goods ordered for
Quantity.freq <- table(Quantity.cut)
rbind(Quantity.freq)
```
...
```{r}
boxplot(Quantity, col= "Red", border= "Blue", 
        main="Qauntity of Goods ordered")
```
...
```{r}
# Quantity Frequency Distribution
hist((Quantity.freq),
     col="red", border=3, 
     main="Quantity Frequency Distribution", 
     xlab="Quantity", 
     ylab="Frequency", 
     axes=T, plot=T, labels=T, right = F)
```
...
```{r}
#Finding the Cumulative frequency distribution of the quantity of goods ordered for
Quantity.cumfreq <- cumsum(Quantity.freq)
rbind(Quantity.cumfreq)
```
...
```{r}
#Checking for the mean regional Total Sales
Regional_Mean_Sales <- rbind(round(sort(tapply(TotalSale, Region, mean),
                                 decreasing = TRUE),2))
Regional_Mean_Sales
```

...
```{r}
#Checking for the mean regional Sales after discount
Regional_Mean_Sales <- rbind(round(sort(tapply(SalesAfterDiscount, Region, mean),
                                 decreasing = TRUE),2))
Regional_Mean_Sales
```
...
```{r}
# finding the corellation between discount and profit
cbind(cor(Discount, Profit))
```
'''
```{r}
plot(Discount, TotalSale,
     col="red", border=3, 
     main="Scatterplot of Discount & Total Sales", 
     xlab="Discount", 
     ylab="Total Sales",
     axes=T, plot=T, labels=T, right = F)
```




STATISTICAL TESTS

```{r}
head(df)
```



ONE SAMPLE T-TEST

```{r}
boxplot(Sales, col= "Red", border= "Blue", 
        main="Box plot Sales")
```

Null Hypothesis (H_0) : Total Sale mean is 1,300 (TotalSale = 1,300)

Alternate hypothesis (H_A) : Total Sale is not 1,300 (TotalSale != 1,300)
```{r}
test_1 <- t.test(TotalSale, mu = 1300)
test_1
```
The p-Value gotten is less than the 0.05 significance level, therefore, the NULL hypothesis is rejected


TWO SAMPLE T-TEST



Null Hypothesis (H_0) : Consumer mean is same as Corporate mean (difference = 0)

Alternate hypothesis (H_A) : Consumer mean is not same as Corporate mean (difference != 0)
```{r}
# assigning the consumer varable to the corresponding TotalSale 
seg_consumer <- Segment == 'Consumer'       # filtering the consumer from the segment column
cons <- df[seg_consumer, ]                     # creates dataset containing Consumer only
consumer_sales <- cons$TotalSale               # selects only the corresponding TotalSale values
```
...
```{r}
# assigningg the corporate data to a viariable 
seg_corporate <- Segment == 'Corporate'    # filtering the corporate from the segment column
corp <- df[seg_corporate, ]                   # creates dataset containing Corpotate only
corporate_sales <- corp$TotalSale             # selects only the corresponding TotalSale values
```

...
```{r}
hist((corporate_sales),
     col="red", border=3, 
     main="Corporate Sales Frequency Distribution", 
     xlab="Sales", 
     ylab="Frequency", 
     axes=T, plot=T, labels=F, right = F)

hist((consumer_sales),
     col="blue", border=3, 
     main="Consumer Sales Frequency Distribution", 
     xlab="Sales", 
     ylab="Frequency", 
     axes=T, plot=T, labels=F, right = F)
```
...
```{r}
# computing the Two sample T-Test
test_2 <- t.test(consumer_sales, corporate_sales, var.equal=TRUE)
test_2
```


as seen above, P-value id greater than 0.05 which makes it not possible to reject the null hypothesis that both means are equal




CHI-SQUARE TEST

```{r}
# The Ship.Mode and Region Contingency Table
ShipRegion_contingency <- with(df, table(Ship.Mode, Region))
cbind(ShipRegion_contingency)
```

...


Null Hypothesis (H_0) : Sales is independent of Discount

Alternate hypothesis (H_A) : Consumer mean is not same as Corporate mean (difference != 0)
```{r}
# implementing the chi-square test
chisq.test(Ship.Mode, Region, correct = FALSE)
```
The p-Value gotten is less than the 0.05 significance level, therefore, the NULL hypothesis is rejected
...




KRUSKAL WALIS TEST
```{r}
cbind(tapply(TotalSale, Order.Priority, median))
```
...
```{r}
#finding the Summary of the four variables
Critical_summary <- summary(TotalSale[Order.Priority=='Critical'])
High_summary <- summary(TotalSale[Order.Priority=='High'])
Low_summary <- summary(TotalSale[Order.Priority=='Low'])
Medium_summary <- summary(TotalSale[Order.Priority=='Medium'])
cbind(Critical_summary, High_summary, Low_summary, Medium_summary)
```
Null Hypothesis (H_0) : same median ranks

Alternate hypothesis (H_A) : at least one of the median rank is different
```{r}
# implementing the Kruskal Walis Test
kruskal.test(Order.Priority ~ TotalSale)
```


as seen above, P-value id grester than 0.05 which makes it not possible to reject the null hypothesis that both median ranks are equal




ANALYSIS OF VARIANCE(ANOVA)
```{r}
df_pie = read.csv('C:/Users/USER/Documents/Raw_Data/meatpie_sales.csv')
head(df_pie, 5)
```


```{r}
boxplot(df_pie, col= "Red", border= "Blue", 
        main="Pie Popularity Box Plot")
```

...
```{r}
# finding the number of rows
nrow(df_pie)
```
...
```{r}
# Concatenate the data rows in df_pie into a single vector.
vec <- c(t(as.matrix(df_pie)))
```
...
```{r}
# Assigning new variables for the treatment levels and number of control blocks.
t_level <- c("ï..Meatpie_A", "Meatpie_B", "Meatpie_c")   # treatment levels 
k <- 3                                             # number of treatment levels 
n <- 45 
```
...
```{r}
m_treatment <- gl(k, 1, n*k, factor(t_level))   # matching treatment 
```
...
```{r}
#creating a vector of blocking factors for each element in the response data.
block_l <- gl(n, k, k*n)             # blocking factor 
```
...
```{r}
# implemnting the ANOVA test 
av <- aov(vec ~ m_treatment + block_l)
summary(av)
```


WILCOXON SIGNED RANK TEST
```{r}
df3 <- read.csv('C:/Users/USER/Documents/Raw_Data/sample_submission.csv')
head(df3, 2)
```
Checking the normality of the distribution
```{r}
# Using the QQ-plot
qqnorm(df3$SalePrice,
      col="red", border=3, 
     main="QQ Plot of Sales", 
     xlab="Sample Quantile", 
     ylab="Theoretical Quantile",
     axes=T, plot=T, labels=T, right = F)
```



The bent line indicates abnormality of the distribution


```{r}
# using KDE plot
d <- density(df3$SalePrice)
plot(d, main="KD Plot of Sales")
polygon(d, col="red", border="blue")
```


The KDE plot also indicates left-skewness.



Using Shapiro-Wilt Test to further check if the data value is normally distributed


Ho = The distribution is normally distributed

Ha = The distribution in not normally distributed

```{r}
# implementing the shapiro wilk test
shapiro.test(df3$SalePrice)
```

Since a p-value extremely lower than 0.05 is gotten, then we can reject the NULL hypothesis that the data value is normally distributed and go ahead with the Wilcoxon signed rank test



Ho = The median(mean) is 180000

Ha = The median(mean) is not 180000
```{r}
wilcox.test(df3$SalePrice, mu = 180000)
```

LINEAR REGRESSION

```{r}
#perform label encoding on variable cegorical variables
df$Segment <- as.numeric(factor(df$Segment))
df$Ship.Mode <- as.numeric(factor(df$Ship.Mode))
df$Region <- as.numeric(factor(df$Region))
df$Order.Priority <- as.numeric(factor(df$Order.Priority))
```


```{r}
head(df, 3)
```

...
```{r}
# the general correlation
cor(df)
```

Ho = the predictors have no influence on the target variables

Ha = the predictors have no influence on the target variables

```{r}
lmr <- lm(Sales ~ Segment + Ship.Mode + Region +Order.Priority + Quantity + Discount)
summary(lmr)

```
...
```{r}
plot(lmr, col = 'red')
```

```{r}

```

